---
title: "Journal (reproducible report)"
author: "Joschka Schwarz"
date: "2020-11-05"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide 131313
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

**IMPORTANT:** You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.

This is an `.Rmd` file. It is plain text with special features. Any time you write just like this, it will be compiled to normal text in the website. If you put a \# in front of your text, it will create a top level-header.

# My first post

Last compiled: `r Sys.Date()`

Notice that whatever you define as a top level header, automatically gets put into the table of contents bar on the left. 

## Second level header

You can add more headers by adding more hashtags. These won't be put into the table of contents

### third level header

Here's an even lower level header

# My second post (note the order)

Last compiled: `r Sys.Date()`

I'm writing this tutorial going from the top down. And, this is how it will be printed. So, notice the second post is second in the list. If you want your most recent post to be at the top, then make a new post starting at the top. If you want the oldest first, do, then keep adding to the bottom

# Adding R stuff


## Tidyverse

### Tasks
```{r}
# SALES ANALYSIS ----

# 1.0 Load libraries ----
library(tidyverse)
library(readxl)
# 2.0 Importing Files ----

# A good convention is to use the file name and suffix it with tbl for the data structure tibble
bikes_tbl      <- read_excel(path = "DS_101/00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel(path = "DS_101/00_data/01_bike_sales/01_raw_data/orderlines.xlsx")

# Not necessary for this analysis, but for the sake of completeness
bikeshops_tbl  <- read_excel(path = "DS_101/00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")


# 3.0 Examining Data ----
orderlines_tbl

glimpse(orderlines_tbl)

# 4.0 Joining Data ----

left_join(orderlines_tbl, bikes_tbl, by = c("product.id" = "bike.id"))

# Chaining commands with the pipe and assigning it to order_items_joined_tbl
bike_orderlines_joined_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))

# Examine the results with glimpse()
bike_orderlines_joined_tbl %>% glimpse()


# 5.0 Wrangling Data ----


# All actions are chained with the pipe already. You can perform each step separately and use glimpse() or View() to validate your code. Store the result in a variable at the end of the steps.
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  # 5.1 Separate category name
  separate(col    = category,
           into   = c("category.1", "category.2", "category.3"),
           sep    = " - ") %>%
  
  # 5.2 Add the total price (price * quantity) 
  # Add a column to a tibble that uses a formula-style calculation of other columns
  mutate(total.price = price * quantity) %>%
  
  # 5.3 Optional: Reorganize. Using select to grab or remove unnecessary columns
  # 5.3.1 by exact column name
  select(-...1, -gender) %>%
  
  # 5.3.2 by a pattern
  # You can use the select_helpers to define patterns. 
  # Type ?ends_with and click on Select helpers in the documentation
  select(-ends_with(".id")) %>%
  
  # 5.3.3 Actually we need the column "order.id". Let's bind it back to the data
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  
  # 5.3.4 You can reorder the data by selecting the columns in your desired order.
  # You can use select_helpers like contains() or everything()
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  
  # 5.4 Rename columns because we actually wanted underscores instead of the dots
  # (one at the time vs. multiple at once)
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))

# 6.0 Business Insights ----
# 6.1 Sales by Year ----

library(lubridate)
# Step 1 - Manipulate
sales_by_year_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Select columns
  select(order_date, total_price) %>%

  # Add year column
  mutate(year = year(order_date)) %>%
  
  # Grouping by year and summarizing sales
  group_by(year) %>% 
  summarize(sales = sum(total_price)) %>%
  
  # Optional: Add a column that turns the numbers into a currency format 
  # (makes it in the plot optically more appealing)
  # mutate(sales_text = scales::dollar(sales)) <- Works for dollar values
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

sales_by_year_tbl


# Step 1 - Manipulate


# Step 2 - Visualize
sales_by_year_tbl %>%
  
  # Setup canvas with the columns year (x-axis) and sales (y-axis)
  ggplot(aes(x = year, y = sales)) +
  
  # Geometries
  geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot
  geom_label(aes(label = sales_text)) + # Adding labels to the bars
  geom_smooth(method = "lm", se = FALSE) + # Adding a trendline
  
  # Formatting
  # scale_y_continuous(labels = scales::dollar) + # Change the y-axis. 
  # Again, we have to adjust it for euro values
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by year",
    subtitle = "Upward Trend",
    x = "", # Override defaults for x and y
    y = "Revenue"
  )



# 6.2 Sales by Year and Category 2 ----


# Step 1 - Manipulate
sales_by_year_cat_1_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Select columns and add a year
  select(order_date, total_price, category_1) %>%
  mutate(year = year(order_date)) %>%
  
  # Group by and summarize year and main catgegory
  group_by(year, category_1) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%
  
  # Format $ Text
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

sales_by_year_cat_1_tbl  

# Step 2 - Visualize
sales_by_year_cat_1_tbl %>%
  
  # Set up x, y, fill
  ggplot(aes(x = year, y = sales, fill = category_1)) +
  
  # Geometries
  geom_col() + # Run up to here to get a stacked bar plot
  
  # Facet
  facet_wrap(~ category_1) +
  
  geom_smooth(method = "lm", se = FALSE) +
  
  # Formatting
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue by year and main category",
    subtitle = "Each product category has an upward trend",
    fill = "Main category" # Changes the legend name
  )


# 7.0 Writing Files ----

# 8.0 Chalange step 1 ----

# Wrangled ----


# All actions are chained with the pipe already. You can perform each step separately and use glimpse() or View() to validate your code. Store the result in a variable at the end of the steps.
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  # 5.1 Separate category name
  separate(col    = category,
           into   = c("category.1", "category.2", "category.3"),
           sep    = " - ") %>%
  ##########
 
  separate(col = location,
           into = c("city", "state"),
           sep = ", ",
           convert = T)   %>% 
  
  ##########
  
  # 5.2 Add the total price (price * quantity) 
  # Add a column to a tibble that uses a formula-style calculation of other columns
  mutate(total.price = price * quantity) %>%
  
  
  # 5.3 Optional: Reorganize. Using select to grab or remove unnecessary columns
  # 5.3.1 by exact column name
  select(-...1, -gender) %>%
  
  # 5.3.2 by a pattern
  # You can use the select_helpers to define patterns. 
  # Type ?ends_with and click on Select helpers in the documentation
  select(-ends_with(".id")) %>%
  
  # 5.3.3 Actually we need the column "order.id". Let's bind it back to the data
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  
  # 5.3.4 You can reorder the data by selecting the columns in your desired order.
  # You can use select_helpers like contains() or everything()
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  
  # 5.4 Rename columns because we actually wanted underscores instead of the dots
  # (one at the time vs. multiple at once)
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))


bike_orderlines_wrangled_tbl

# First set ----

sales_by_state_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Select columns
  select(state, total_price) %>%
  
  # Add year column
  #mutate(year = year(order_date)) %>%
  
  # Grouping by year and summarizing sales
  group_by(state) %>% 
  summarize(sales = sum(total_price)) %>%
  
  # Optional: Add a column that turns the numbers into a currency format 
  # (makes it in the plot optically more appealing)
  # mutate(sales_text = scales::dollar(sales)) <- Works for dollar values
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

sales_by_state_tbl


# First Plot ----
#{r plot, fig.width=10, fig.height=7}
sales_by_state_tbl %>%
  
  # Setup canvas with the columns year (x-axis) and sales (y-axis)
  ggplot(aes(x = state, y = sales)) +
  
  # Geometries
  geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot
  geom_label(aes(label = sales_text)) + # Adding labels to the bars
  geom_smooth(method = "lm", se = FALSE) + # Adding a trendline
  
  
  
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +

  # Formatting
  # scale_y_continuous(labels = scales::dollar) + # Change the y-axis. 
  # Again, we have to adjust it for euro values
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by State",
    subtitle = "Upward Trend",
    x = "", # Override defaults for x and y
    y = "Revenue"
  )

# 9.0 Chalange step 2 ----

sales_by_year_state_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Select columns and add a year
  select(order_date, total_price, state) %>%
  mutate(year = year(order_date)) %>%
  
  # Group by and summarize year and main catgegory
  group_by(year, state) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%
  
  # Format $ Text
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

sales_by_year_state_tbl  

# Second Plot ----

sales_by_year_state_tbl %>%
  
  # Set up x, y, fill
  ggplot(aes(x = year, y = sales, fill = state)) +
  
  # Geometries
  geom_col() + # Run up to here to get a stacked bar plot
  
  # Facet
  facet_wrap(~ state) +
  
  geom_smooth(method = "lm", se = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # Formatting
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue by year and State",
    subtitle = "Each state has an upward trend",
    fill = "States" # Changes the legend name
  )


# 7.1 Excel ----
#install.packages("writexl")
#library("writexl")
#bike_orderlines_wrangled_tbl %>%
#  write_xlsx("DS_101/00_data/01_bike_sales/02_wrangled_data/bike_orderlines.xlsx")

# 7.2 CSV ----
#bike_orderlines_wrangled_tbl %>% 
#  write_csv("DS_101/00_data/01_bike_sales/02_wrangled_data/bike_orderlines.csv")

# 7.3 RDS ----
#bike_orderlines_wrangled_tbl %>% 
#  write_rds("DS_101/00_data/01_bike_sales/02_wrangled_data/bike_orderlines.rds")

```

## Data acquisition
### API task
```{r}
# 1.0 LIBRARIES ----

library(tidyverse) # Main Package - Loads dplyr, purrr, etc.
library(rvest)     # HTML Hacking & Web Scraping
library(xopen)     # Quickly opening URLs
library(jsonlite)  # converts JSON files to R objects
library(glue)      # concatenate strings
library(stringi)   # character string/text processing
library(httr)
library(RSQLite)



# get some date, make a tibble, print some of it 

resp <- GET("http://openlibrary.org/people/george08/lists/OL97L/seeds.json")

resp
#rawToChar(resp$content)



resp %>% 
  .$content %>% 
  rawToChar() %>% 
  fromJSON()

data_lst <- fromJSON("http://openlibrary.org/people/george08/lists/OL97L/seeds.json")
# Open the data by clicking on it in the environment or by running View()
#View(data_lst)

# the tibble ----
title<-data_lst%>%
  purrr::pluck("entries", "title")
work_count<-data_lst%>%
  purrr::pluck("entries", "work_count")
edition_count<-data_lst%>%
  purrr::pluck("entries", "edition_count")
ebook_count<-data_lst%>%
  purrr::pluck("entries", "ebook_count")

tibble(title ,work_count ,edition_count ,ebook_count)

```




### Scraping task
```{r}

# 1.0 LIBRARIES ----

library(tidyverse) # Main Package - Loads dplyr, purrr, etc.
library(rvest)     # HTML Hacking & Web Scraping
library(xopen)     # Quickly opening URLs
library(jsonlite)  # converts JSON files to R objects
library(glue)      # concatenate strings
library(stringi)   # character string/text processing
library(httr)
library(RSQLite)
library(ggplot2)
library(dplyr)


# create small database: model names and price of 
#                        at least one category


#xopen(url_home) # Open links directly from RStudio to inspect them

url  <- "https://www.radon-bikes.de/en/trekking-cross/cross/bikegrid/"
html <- url %>% 
  read_html()

names <-  html %>% 
  html_nodes(css = ".a-heading.a-heading--small") %>% 
  html_text() %>% 
  stringr::str_extract("(?<= ).*(?=)")%>%
  discard(.p = ~stringr::str_detect(.x,"to our Radon-Bikes Instagram!|#bisbaldimwald"))
  #purrr::discard(names,.p = ~stringr::str_detect(.x,"to our Radon-Bikes Instagram!|#bisbaldimwald"))
names


price <-  html %>% 
  #html_nodes(css = ".m-bikegrid__price.currency_eur >span") %>% 
  html_nodes(css = ".m-bikegrid__price--active") %>% 
  html_text() %>% 
  #html_attr("class")%>%
  stringr::str_extract("(?<=).*(?=)") %>%
  discard(.p = ~stringr::str_detect(.x," ₤"))%>%
  as_tibble()%>%
  filter(row_number() %% 2 == 1)

price


tibble(Model=names, Cost=price)

## tidyverse
```{r}
# Libraries ----

# Tidyverse
library(tidyverse)
library(vroom)

# Data Table
library(data.table)

# Counter
library(tictoc)

library(vroom)
```
## Data wrangling
### Tasks 1
```{r}
# first task ----

library(vroom)

col_types_assignee <- list(
  id = col_character(),
  type = col_integer(),
  name_first= col_skip(),
  name_last = col_skip(),
  organization = col_character()
)

assignee_tbl <- vroom(
 # file       = "/DS_101/00_data_wrangling/assignee.tsv",
   file       = "assignee.tsv",
  delim      = "\t", 
  col_types  = col_types_assignee,
  na         = c("", "NA", "NULL")
)

assignee_tbl

setDT(assignee_tbl)

assignee_tbl %>% glimpse()




          col_types_patent_assignee <- list(
            patent_id = col_character(),
            assignee_id = col_character(),
            location_id = col_skip()
          )
          
          patent_assignee_tbl <- vroom(
            file       = "patent_assignee.tsv", 
            delim      = "\t", 
            col_types  = col_types_patent_assignee,
            na         = c("", "NA", "NULL")
          )



patent_assignee_tbl

setDT(patent_assignee_tbl)

patent_assignee_tbl %>% glimpse()



tic()
patent_assignee_assignee_tbl <- merge(x = patent_assignee_tbl, y = assignee_tbl, 
                      by.x = "assignee_id", by.y = "id",
                      all.x = TRUE, 
                      all.y = TRUE)
toc()

patent_assignee_assignee_tbl %>% glimpse()

patent_assignee_assignee_tbl



setkey(patent_assignee_assignee_tbl, "type")
key(patent_assignee_assignee_tbl)

?setorder()
setorderv(patent_assignee_assignee_tbl, c("type", "organization"))


patent_assignee_assignee_tbl_us <- patent_assignee_assignee_tbl[ (type == 2)]

patent_assignee_assignee_tbl_us


tic()
most_patents_us <- patent_assignee_assignee_tbl_us[!is.na(organization), .N, by = organization]
toc()


setkey(most_patents_us, "organization")
key(most_patents_us)

setorderv(most_patents_us, c("N", "organization"), order = -1)



as_tibble(most_patents_us, .rows = 10)

#Patent Dominance: What US company / 
#corporation has the most patents? 
#List the 10 US companies with the 
#most assigned/granted patents.

# use data.table  or dplyr
# tables needed: assignee, patent_assignee
```
### Tasks 2
```{r}
# second task ----



col_types_patent <- list(
  id = col_character(),
  date = col_date("%Y-%m-%d"),
  num_claims = col_integer(),
  type = col_skip(),
  number = col_skip(),
  country = col_skip(),
  abstract = col_skip(),
  kind = col_skip(),
  filename = col_skip(),
  withdrawn = col_skip(),
  title = col_skip()
)

patent_tbl <- vroom(
 # file       = "/DS_101/00_data_wrangling/patent.tsv",
  file       = "patent.tsv",
  delim      = "\t", 
  col_types  = col_types_patent,
  na         = c("", "NA", "NULL")
)


setDT(patent_tbl)

patent_tbl %>% glimpse()

tic()
patent_assignee_assignee_patent_tbl <- merge(x = patent_assignee_assignee_tbl, y = patent_tbl,
                      by.x = "patent_id", by.y = "id",
                      all.x = TRUE,
                      all.y = TRUE)

toc()

patent_assignee_assignee_patent_tbl %>% glimpse()


setkey(patent_assignee_assignee_patent_tbl, "type")
key(patent_assignee_assignee_patent_tbl)

?setorder()
setorderv(patent_assignee_assignee_patent_tbl, c("type", "organization"))


patent_assignee_assignee_patent_us2 <- patent_assignee_assignee_patent_tbl[ (type == '2') ]

patent_assignee_assignee_patent_year <- patent_assignee_assignee_patent_us2 %>%
  select(organization, num_claims, date) %>%
  mutate(year = year(date))


patent_assignee_assignee_patent_year



patent_assignee_assignee_patent_2019 <- patent_assignee_assignee_patent_year[ (year == '2019') ]

setkey(patent_assignee_assignee_patent_2019, "organization")
key(patent_assignee_assignee_patent_2019)

setorderv(patent_assignee_assignee_patent_2019, c("num_claims", "organization"), order = -1)

task_2_ans <- patent_assignee_assignee_patent_2019 %>%
  select(organization, num_claims, date)

as_tibble(task_2_ans, .rows = 10)


#Recent patent activity: What US company
#had the most patents granted in 2019?
#List the top 10 companies with the 
#most new granted patents for 2019.

# use data.table  or dplyr
# tables needed: assignee, patent_assignee, patent
```
### Tasks 3
```{r}
# third task ----



col_types_uspc <- list(
  patent_id = col_character(),
  mainclass_id = col_character(),
  sequence = col_integer(),
  uuid = col_skip(),
  subclass_id = col_skip()
  
)

uspc_tbl <- vroom(
#  file       = "/DS_101/00_data_wrangling/uspc.tsv",
  file       = "uspc.tsv",
  delim      = "\t", 
  col_types  = col_types_uspc,
  na         = c("", "NA", "NULL")
)

setDT(uspc_tbl)

uspc_tbl %>% glimpse()


tic()
patent_assignee_assignee_uspc_tbl <- merge(x = patent_assignee_assignee_tbl, y = uspc_tbl,
                      by = "patent_id",
                      all.x = TRUE,  
                      all.y = TRUE)
toc()

patent_assignee_assignee_uspc_tbl %>% glimpse()

            setkey(patent_assignee_assignee_tbl, "type")
            key(patent_assignee_assignee_tbl)
            
            ?setorder()
            setorderv(patent_assignee_assignee_tbl, c("type", "organization"))
            
            
            patent_assignee_assignee_tbl_us <- patent_assignee_assignee_tbl[ (type == 2)|(type == 3)]
            
            patent_assignee_assignee_tbl_us
            
            
            tic()
            most_patents_world <- patent_assignee_assignee_tbl_us[!is.na(organization), .N, by = organization]
            toc()
            
            
            setkey(most_patents_world, "organization")
            key(most_patents_world)
            
            setorderv(most_patents_world, c("N", "organization"), order = -1)
            
            
            
            as_tibble(most_patents_world, .rows = 10)

            
            
setkey(patent_assignee_assignee_uspc_tbl, "mainclass_id")
key(patent_assignee_assignee_uspc_tbl)

?setorder()
setorderv(patent_assignee_assignee_uspc_tbl, c("mainclass_id"))
patent_assignee_assignee_uspc_tbl

patent_assignee_assignee_uspc_tbl_world <- patent_assignee_assignee_uspc_tbl[!(mainclass_id == 'na')]
patent_assignee_assignee_uspc_tbl_world <- patent_assignee_assignee_uspc_tbl_world[(organization == 'International Business Machines Corporation')|
                                                                                   (organization == 'Samsung Electronics Co., Ltd.')|
                                                                                   (organization == 'Canon Kabushiki Kaisha')|
                                                                                   (organization == 'Sony Corporation')|
                                                                                   (organization == 'Kabushiki Kaisha Toshiba')|
                                                                                   (organization == 'General Electric Company')|
                                                                                   (organization == 'Hitachi, Ltd.')|
                                                                                   (organization == 'Intel Corporation')|
                                                                                   (organization == 'Fujitsu Limited')|
                                                                                   (organization == 'Hewlett-Packard Development Company, L.P.')]          
          
tic()
top_patent_class <- patent_assignee_assignee_uspc_tbl_world[!is.na(mainclass_id), .N, by = mainclass_id]
toc()

top_patent_class

setkey(top_patent_class, "mainclass_id")
key(top_patent_class)

setorderv(top_patent_class, c("N", "mainclass_id"), order = -1)



as_tibble(top_patent_class, .rows = 5)


          
          
#Innovation in Tech: What is 
#the most innovative tech sector? 
#For the top 10 companies (worldwide) 
#with the most patents, what are the 
#top 5 USPTO tech main classes?

# use data.table  or dplyr
# tables needed: assignee, patent_assignee, uspc
```
