---
title: "Journal (reproducible report)"
author: "Joschka Schwarz"
date: "2020-11-05"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide 131313
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```


# Compilet dates

Last compiled: `r Sys.Date()`


Last compiled: `r Sys.Date()`






# Tidyverse

```{r}
# SALES ANALYSIS ----

# 1.0 Load libraries ----
library(tidyverse)
library(readxl)
# 2.0 Importing Files ----

# A good convention is to use the file name and suffix it with tbl for the data structure tibble
bikes_tbl      <- read_excel(path = "DS_101/00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel(path = "DS_101/00_data/01_bike_sales/01_raw_data/orderlines.xlsx")

# Not necessary for this analysis, but for the sake of completeness
bikeshops_tbl  <- read_excel(path = "DS_101/00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")


# 3.0 Examining Data ----
orderlines_tbl

glimpse(orderlines_tbl)

# 4.0 Joining Data ----

left_join(orderlines_tbl, bikes_tbl, by = c("product.id" = "bike.id"))

# Chaining commands with the pipe and assigning it to order_items_joined_tbl
bike_orderlines_joined_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))

# Examine the results with glimpse()
bike_orderlines_joined_tbl %>% glimpse()


# 5.0 Wrangling Data ----


# All actions are chained with the pipe already. You can perform each step separately and use glimpse() or View() to validate your code. Store the result in a variable at the end of the steps.
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  # 5.1 Separate category name
  separate(col    = category,
           into   = c("category.1", "category.2", "category.3"),
           sep    = " - ") %>%
  
  # 5.2 Add the total price (price * quantity) 
  # Add a column to a tibble that uses a formula-style calculation of other columns
  mutate(total.price = price * quantity) %>%
  
  # 5.3 Optional: Reorganize. Using select to grab or remove unnecessary columns
  # 5.3.1 by exact column name
  select(-...1, -gender) %>%
  
  # 5.3.2 by a pattern
  # You can use the select_helpers to define patterns. 
  # Type ?ends_with and click on Select helpers in the documentation
  select(-ends_with(".id")) %>%
  
  # 5.3.3 Actually we need the column "order.id". Let's bind it back to the data
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  
  # 5.3.4 You can reorder the data by selecting the columns in your desired order.
  # You can use select_helpers like contains() or everything()
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  
  # 5.4 Rename columns because we actually wanted underscores instead of the dots
  # (one at the time vs. multiple at once)
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))

# 6.0 Business Insights ----
# 6.1 Sales by Year ----

library(lubridate)
# Step 1 - Manipulate
sales_by_year_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Select columns
  select(order_date, total_price) %>%

  # Add year column
  mutate(year = year(order_date)) %>%
  
  # Grouping by year and summarizing sales
  group_by(year) %>% 
  summarize(sales = sum(total_price)) %>%
  
  # Optional: Add a column that turns the numbers into a currency format 
  # (makes it in the plot optically more appealing)
  # mutate(sales_text = scales::dollar(sales)) <- Works for dollar values
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

sales_by_year_tbl


# Step 1 - Manipulate


# Step 2 - Visualize
sales_by_year_tbl %>%
  
  # Setup canvas with the columns year (x-axis) and sales (y-axis)
  ggplot(aes(x = year, y = sales)) +
  
  # Geometries
  geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot
  geom_label(aes(label = sales_text)) + # Adding labels to the bars
  geom_smooth(method = "lm", se = FALSE) + # Adding a trendline
  
  # Formatting
  # scale_y_continuous(labels = scales::dollar) + # Change the y-axis. 
  # Again, we have to adjust it for euro values
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by year",
    subtitle = "Upward Trend",
    x = "", # Override defaults for x and y
    y = "Revenue"
  )



# 6.2 Sales by Year and Category 2 ----


# Step 1 - Manipulate
sales_by_year_cat_1_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Select columns and add a year
  select(order_date, total_price, category_1) %>%
  mutate(year = year(order_date)) %>%
  
  # Group by and summarize year and main catgegory
  group_by(year, category_1) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%
  
  # Format $ Text
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

sales_by_year_cat_1_tbl  

# Step 2 - Visualize
sales_by_year_cat_1_tbl %>%
  
  # Set up x, y, fill
  ggplot(aes(x = year, y = sales, fill = category_1)) +
  
  # Geometries
  geom_col() + # Run up to here to get a stacked bar plot
  
  # Facet
  facet_wrap(~ category_1) +
  
  geom_smooth(method = "lm", se = FALSE) +
  
  # Formatting
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue by year and main category",
    subtitle = "Each product category has an upward trend",
    fill = "Main category" # Changes the legend name
  )


# 7.0 Writing Files ----

# 8.0 Chalange step 1 ----

# Wrangled ----


# All actions are chained with the pipe already. You can perform each step separately and use glimpse() or View() to validate your code. Store the result in a variable at the end of the steps.
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  # 5.1 Separate category name
  separate(col    = category,
           into   = c("category.1", "category.2", "category.3"),
           sep    = " - ") %>%
  ##########
 
  separate(col = location,
           into = c("city", "state"),
           sep = ", ",
           convert = T)   %>% 
  
  ##########
  
  # 5.2 Add the total price (price * quantity) 
  # Add a column to a tibble that uses a formula-style calculation of other columns
  mutate(total.price = price * quantity) %>%
  
  
  # 5.3 Optional: Reorganize. Using select to grab or remove unnecessary columns
  # 5.3.1 by exact column name
  select(-...1, -gender) %>%
  
  # 5.3.2 by a pattern
  # You can use the select_helpers to define patterns. 
  # Type ?ends_with and click on Select helpers in the documentation
  select(-ends_with(".id")) %>%
  
  # 5.3.3 Actually we need the column "order.id". Let's bind it back to the data
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  
  # 5.3.4 You can reorder the data by selecting the columns in your desired order.
  # You can use select_helpers like contains() or everything()
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  
  # 5.4 Rename columns because we actually wanted underscores instead of the dots
  # (one at the time vs. multiple at once)
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))


bike_orderlines_wrangled_tbl

# First set ----

sales_by_state_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Select columns
  select(state, total_price) %>%
  
  # Add year column
  #mutate(year = year(order_date)) %>%
  
  # Grouping by year and summarizing sales
  group_by(state) %>% 
  summarize(sales = sum(total_price)) %>%
  
  # Optional: Add a column that turns the numbers into a currency format 
  # (makes it in the plot optically more appealing)
  # mutate(sales_text = scales::dollar(sales)) <- Works for dollar values
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

sales_by_state_tbl


# First Plot ----
#{r plot, fig.width=10, fig.height=7}
sales_by_state_tbl %>%
  
  # Setup canvas with the columns year (x-axis) and sales (y-axis)
  ggplot(aes(x = state, y = sales)) +
  
  # Geometries
  geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot
  geom_label(aes(label = sales_text)) + # Adding labels to the bars
  geom_smooth(method = "lm", se = FALSE) + # Adding a trendline
  
  
  
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +

  # Formatting
  # scale_y_continuous(labels = scales::dollar) + # Change the y-axis. 
  # Again, we have to adjust it for euro values
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by State",
    subtitle = "Upward Trend",
    x = "", # Override defaults for x and y
    y = "Revenue"
  )

# 9.0 Chalange step 2 ----

sales_by_year_state_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Select columns and add a year
  select(order_date, total_price, state) %>%
  mutate(year = year(order_date)) %>%
  
  # Group by and summarize year and main catgegory
  group_by(year, state) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%
  
  # Format $ Text
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

sales_by_year_state_tbl  

# Second Plot ----

sales_by_year_state_tbl %>%
  
  # Set up x, y, fill
  ggplot(aes(x = year, y = sales, fill = state)) +
  
  # Geometries
  geom_col() + # Run up to here to get a stacked bar plot
  
  # Facet
  facet_wrap(~ state) +
  
  geom_smooth(method = "lm", se = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # Formatting
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue by year and State",
    subtitle = "Each state has an upward trend",
    fill = "States" # Changes the legend name
  )


# 7.1 Excel ----
#install.packages("writexl")
#library("writexl")
#bike_orderlines_wrangled_tbl %>%
#  write_xlsx("DS_101/00_data/01_bike_sales/02_wrangled_data/bike_orderlines.xlsx")

# 7.2 CSV ----
#bike_orderlines_wrangled_tbl %>% 
#  write_csv("DS_101/00_data/01_bike_sales/02_wrangled_data/bike_orderlines.csv")

# 7.3 RDS ----
#bike_orderlines_wrangled_tbl %>% 
#  write_rds("DS_101/00_data/01_bike_sales/02_wrangled_data/bike_orderlines.rds")

```

# Data acquisition
## API task
```{r}
# 1.0 LIBRARIES ----

library(tidyverse) # Main Package - Loads dplyr, purrr, etc.
library(rvest)     # HTML Hacking & Web Scraping
library(xopen)     # Quickly opening URLs
library(jsonlite)  # converts JSON files to R objects
library(glue)      # concatenate strings
library(stringi)   # character string/text processing
library(httr)
library(RSQLite)



# get some date, make a tibble, print some of it 

resp <- GET("http://openlibrary.org/people/george08/lists/OL97L/seeds.json")

resp
#rawToChar(resp$content)



resp %>% 
  .$content %>% 
  rawToChar() %>% 
  fromJSON()

data_lst <- fromJSON("http://openlibrary.org/people/george08/lists/OL97L/seeds.json")
# Open the data by clicking on it in the environment or by running View()
#View(data_lst)

# the tibble ----
title<-data_lst%>%
  purrr::pluck("entries", "title")
work_count<-data_lst%>%
  purrr::pluck("entries", "work_count")
edition_count<-data_lst%>%
  purrr::pluck("entries", "edition_count")
ebook_count<-data_lst%>%
  purrr::pluck("entries", "ebook_count")
```














A table from a random API 
```{r}
tibble(title ,work_count ,edition_count ,ebook_count)

```




## Scraping task
```{r}

# 1.0 LIBRARIES ----

library(tidyverse) # Main Package - Loads dplyr, purrr, etc.
library(rvest)     # HTML Hacking & Web Scraping
library(xopen)     # Quickly opening URLs
library(jsonlite)  # converts JSON files to R objects
library(glue)      # concatenate strings
library(stringi)   # character string/text processing
library(httr)
library(RSQLite)
library(ggplot2)
library(dplyr)


# create small database: model names and price of 
#                        at least one category


#xopen(url_home) # Open links directly from RStudio to inspect them

url  <- "https://www.radon-bikes.de/en/trekking-cross/cross/bikegrid/"
html <- url %>% 
  read_html()

names <-  html %>% 
  html_nodes(css = ".a-heading.a-heading--small") %>% 
  html_text() %>% 
  stringr::str_extract("(?<= ).*(?=)")%>%
  #discard(.p = ~stringr::str_detect(.x,"to our Radon-Bikes Instagram!|#bisbaldimwald"))
  purrr::discard(names,.p = ~stringr::str_detect(.x,"to our Radon-Bikes Instagram!|#bisbaldimwald"))
names


price <-  html %>% 
  #html_nodes(css = ".m-bikegrid__price.currency_eur >span") %>% 
  html_nodes(css = ".m-bikegrid__price--active") %>% 
  html_text() %>% 
  #html_attr("class")%>%
  stringr::str_extract("(?<=).*(?=)") %>%
  purrr::discard(names,.p = ~stringr::str_detect(.x," ₤"))%>%
  as_tibble()%>%
  filter(row_number() %% 2 == 1)

price

```












Bike names and price in euros












```{r}

tibble(Model=names, "Cost  "=price)
```

# Data wrangling
```{r}
# Libraries ----

# Tidyverse
library(tidyverse)
library(vroom)

# Data Table
library(data.table)

# Counter
library(tictoc)

library(vroom)

```
## Tasks 1
```{r}
# first task ----


col_types_assignee <- list(
  id = col_character(),
  type = col_integer(),
  name_first= col_skip(),
  name_last = col_skip(),
  organization = col_character()
)

assignee_tbl <- vroom(
 # file       = "/DS_101/00_data_wrangling/assignee.tsv",
   file       = "assignee.tsv",
  delim      = "\t", 
  col_types  = col_types_assignee,
  na         = c("", "NA", "NULL")
)

assignee_tbl

setDT(assignee_tbl)

assignee_tbl %>% glimpse()




          col_types_patent_assignee <- list(
            patent_id = col_character(),
            assignee_id = col_character(),
            location_id = col_skip()
          )
          
          patent_assignee_tbl <- vroom(
            file       = "patent_assignee.tsv", 
            delim      = "\t", 
            col_types  = col_types_patent_assignee,
            na         = c("", "NA", "NULL")
          )



patent_assignee_tbl

setDT(patent_assignee_tbl)

patent_assignee_tbl %>% glimpse()



tic()
patent_assignee_assignee_tbl <- merge(x = patent_assignee_tbl, y = assignee_tbl, 
                      by.x = "assignee_id", by.y = "id",
                      all.x = TRUE, 
                      all.y = TRUE)
toc()

patent_assignee_assignee_tbl %>% glimpse()

patent_assignee_assignee_tbl



setkey(patent_assignee_assignee_tbl, "type")
key(patent_assignee_assignee_tbl)

?setorder()
setorderv(patent_assignee_assignee_tbl, c("type", "organization"))


patent_assignee_assignee_tbl_us <- patent_assignee_assignee_tbl[ (type == 2)]

patent_assignee_assignee_tbl_us


tic()
most_patents_us <- patent_assignee_assignee_tbl_us[!is.na(organization), .N, by = organization]
toc()


setkey(most_patents_us, "organization")
key(most_patents_us)

setorderv(most_patents_us, c("N", "organization"), order = -1)

```













Patent Dominance: What US company / corporation has the most patents? 
List the 10 US companies with the most assigned/granted patents.












```{r}

as_tibble(most_patents_us, .rows = 10)

# use data.table  or dplyr
# tables needed: assignee, patent_assignee
```
## Tasks 2
```{r}
# second task ----



col_types_patent <- list(
  id = col_character(),
  date = col_date("%Y-%m-%d"),
  num_claims = col_integer(),
  type = col_skip(),
  number = col_skip(),
  country = col_skip(),
  abstract = col_skip(),
  kind = col_skip(),
  filename = col_skip(),
  withdrawn = col_skip(),
  title = col_skip()
)

patent_tbl <- vroom(
 # file       = "/DS_101/00_data_wrangling/patent.tsv",
  file       = "patent.tsv",
  delim      = "\t", 
  col_types  = col_types_patent,
  na         = c("", "NA", "NULL")
)


setDT(patent_tbl)

patent_tbl %>% glimpse()

tic()
patent_assignee_assignee_patent_tbl <- merge(x = patent_assignee_assignee_tbl, y = patent_tbl,
                      by.x = "patent_id", by.y = "id",
                      all.x = TRUE,
                      all.y = TRUE)

toc()

patent_assignee_assignee_patent_tbl %>% glimpse()


setkey(patent_assignee_assignee_patent_tbl, "type")
key(patent_assignee_assignee_patent_tbl)

?setorder()
setorderv(patent_assignee_assignee_patent_tbl, c("type", "organization"))


patent_assignee_assignee_patent_us2 <- patent_assignee_assignee_patent_tbl[ (type == '2') ]

patent_assignee_assignee_patent_year <- patent_assignee_assignee_patent_us2 %>%
  select(organization, num_claims, date) %>%
  mutate(year = year(date))


patent_assignee_assignee_patent_year



patent_assignee_assignee_patent_2019 <- patent_assignee_assignee_patent_year[ (year == '2019') ]

setkey(patent_assignee_assignee_patent_2019, "organization")
key(patent_assignee_assignee_patent_2019)

setorderv(patent_assignee_assignee_patent_2019, c("num_claims", "organization"), order = -1)

task_2_ans <- patent_assignee_assignee_patent_2019 %>%
  select(organization, num_claims, date)


```









Recent patent activity: What US company
had the most patents granted in 2019?
List the top 10 companies with the 
most new granted patents for 2019.










```{r}

as_tibble(task_2_ans, .rows = 10)


# use data.table  or dplyr
# tables needed: assignee, patent_assignee, patent
```
## Tasks 3
```{r}
# third task ----



col_types_uspc <- list(
  patent_id = col_character(),
  mainclass_id = col_character(),
  sequence = col_integer(),
  uuid = col_skip(),
  subclass_id = col_skip()
  
)

uspc_tbl <- vroom(
#  file       = "/DS_101/00_data_wrangling/uspc.tsv",
  file       = "uspc.tsv",
  delim      = "\t", 
  col_types  = col_types_uspc,
  na         = c("", "NA", "NULL")
)

setDT(uspc_tbl)

uspc_tbl %>% glimpse()


tic()
patent_assignee_assignee_uspc_tbl <- merge(x = patent_assignee_assignee_tbl, y = uspc_tbl,
                      by = "patent_id",
                      all.x = TRUE,  
                      all.y = TRUE)
toc()

patent_assignee_assignee_uspc_tbl %>% glimpse()

            setkey(patent_assignee_assignee_tbl, "type")
            key(patent_assignee_assignee_tbl)
            
            ?setorder()
            setorderv(patent_assignee_assignee_tbl, c("type", "organization"))
            
            
            patent_assignee_assignee_tbl_us <- patent_assignee_assignee_tbl[ (type == 2)|(type == 3)]
            
            patent_assignee_assignee_tbl_us
            
            
            tic()
            most_patents_world <- patent_assignee_assignee_tbl_us[!is.na(organization), .N, by = organization]
            toc()
            
            
            setkey(most_patents_world, "organization")
            key(most_patents_world)
            
            setorderv(most_patents_world, c("N", "organization"), order = -1)
            
```









top 10 most patent holding companies world wide









```{r}            
            
            as_tibble(most_patents_world, .rows = 10)

            
            
setkey(patent_assignee_assignee_uspc_tbl, "mainclass_id")
key(patent_assignee_assignee_uspc_tbl)

?setorder()
setorderv(patent_assignee_assignee_uspc_tbl, c("mainclass_id"))
patent_assignee_assignee_uspc_tbl

patent_assignee_assignee_uspc_tbl_world <- patent_assignee_assignee_uspc_tbl[!(mainclass_id == 'na')]
patent_assignee_assignee_uspc_tbl_world <- patent_assignee_assignee_uspc_tbl_world[(organization == 'International Business Machines Corporation')|
                                                                                   (organization == 'Samsung Electronics Co., Ltd.')|
                                                                                   (organization == 'Canon Kabushiki Kaisha')|
                                                                                   (organization == 'Sony Corporation')|
                                                                                   (organization == 'Kabushiki Kaisha Toshiba')|
                                                                                   (organization == 'General Electric Company')|
                                                                                   (organization == 'Hitachi, Ltd.')|
                                                                                   (organization == 'Intel Corporation')|
                                                                                   (organization == 'Fujitsu Limited')|
                                                                                   (organization == 'Hewlett-Packard Development Company, L.P.')]          
          
tic()
top_patent_class <- patent_assignee_assignee_uspc_tbl_world[!is.na(mainclass_id), .N, by = mainclass_id]
toc()

top_patent_class

setkey(top_patent_class, "mainclass_id")
key(top_patent_class)

setorderv(top_patent_class, c("N", "mainclass_id"), order = -1)
```








most common patent out of top 10 companies










```{r}

as_tibble(top_patent_class, .rows = 5)


          
          
#Innovation in Tech: What is 
#the most innovative tech sector? 
#For the top 10 companies (worldwide) 
#with the most patents, what are the 
#top 5 USPTO tech main classes?
```












Innovation in Tech: What is the most innovative tech sector? 
For the top 10 companies (worldwide) with the most patents, what are the 
top 5 USPTO tech main classes?.











```{r}
# use data.table  or dplyr
# tables needed: assignee, patent_assignee, uspc
```
# Data visualisation 


```{r}

#Goal: Map the time course of the cumulative Covid-19 cases! 
#Adding the cases for Europe is optional. You can choose your 
#own color theme, but don’t use the default one. Don’t forget 
#to scale the axis properly. The labels can be added with 
#geom_label() or with geom_label_repel() 
#(from the package ggrepel).



# Challenge 4----

#Covid data analysis


library(tidyverse)
library(vroom)
library(lubridate)
library(data.table)
library(tictoc)
library(ggplot2)
library(scales)


covid_data_tbl <- read_csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv")




#{r include=FALSE}
covid_data_by_month_tbl <- covid_data_tbl %>% map_df(rev)%>%
  select(cases_weekly, countriesAndTerritories, dateRep) %>%
  filter(countriesAndTerritories %in% c("Germany",
                                        "United_Kingdom",
                                        "France",
                                        "Spain",
                                        "Lithuania",
                                        "United_States_of_America")) %>%
  mutate(date = dmy(dateRep)) %>% group_by(countriesAndTerritories ) %>%
  mutate(total_cases = cumsum(cases_weekly))# %>%
  #ungroup() 
  
covid_data_by_month_tbl 

  tbl <- covid_data_tbl %>% map_df(rev)%>%
  select(dateRep, countriesAndTerritories, cases_weekly) %>%
  filter(countriesAndTerritories %in% c("Germany",
                                        "United_Kingdom",
                                        "France",
                                        "Spain",
                                        "Lithuania",
                                        "United_States_of_America")) %>% 
    group_by( countriesAndTerritories ) %>% 
  mutate(total_cases = cumsum(cases_weekly))# %>% map_df(rev) 
 tbl
 tbl2 <- tbl[4]

tbl2  
  
#total <- merge(covid_data_by_month_tbl, tbl)

#total %>% group_by(countriesAndTerritories, date) %>% ungroup() 

#total


#Covid cases ----
```










Covid graph for few countries











```{r}
#{r plot5, fig.width=15, fig.height=7, echo=FALSE}
covid_data_by_month_tbl%>%
  ggplot(aes(x = date, y = total_cases, color = countriesAndTerritories)) +
  #geom_line()+
  #facet_wrap(~ countriesAndTerritories, ncol = 3) +
  geom_smooth(method = "gam", se = FALSE) +
  #geom_point()+
  scale_color_manual(values=c("#000000", "#ff0016", "#3ea6d7", "#feff00", "#106a00", "#ff8e02"))+
  labs(title = "Confirmed covid cases worldwide",
       x = "Year 2020",
       y = "Cases")




#{r include=FALSE}


#Goal: Visualize the distribution of the mortality rate
#(deaths / population) with geom_map().

# World Map ----

world <- map_data("world")

covid_mortality_tbl <- covid_data_tbl %>% # map_df(rev)%>%
  mutate(across(countriesAndTerritories, str_replace_all, "_", " ")) %>%
  mutate(countriesAndTerritories = case_when(
    
    countriesAndTerritories == "United Kingdom" ~ "UK",
    countriesAndTerritories == "United States of America" ~ "USA",
    countriesAndTerritories == "Czechia" ~ "Czech Republic",
    TRUE ~ countriesAndTerritories
    
  ))%>%
  group_by(countriesAndTerritories, popData2019, deaths_weekly) %>%
  summarise(total_pop = max(popData2019))%>%
  mutate(total_death = sum(deaths_weekly))%>%
  mutate(mortality =  (total_death)/(popData2019))



#{r include=FALSE}

#class(covid_mortality_tbl)

setDT(covid_mortality_tbl)

#class(covid_mortality_tbl)
covid_mortality_tbl
covid_mortality_tbl %>% glimpse()

setDT(world)

world %>% glimpse()


#{r include=FALSE}
tic()
covid_map_tbl <- merge(x = world, y = covid_mortality_tbl, 
                       by.x = "region", by.y = "countriesAndTerritories",
                       all.x = TRUE, 
                       all.y = FALSE,
                       allow.cartesian=TRUE)

toc()

covid_map_tbl%>% glimpse()





#{r include=FALSE}
setkey(covid_map_tbl, "region")
key(covid_map_tbl)

setorderv(covid_map_tbl, c("mortality", "region", "long", "lat"), order = -1)


```














Covid map












```{r}
#{r plot6, fig.width=15, fig.height=7, echo=FALSE}
covid_map_tbl%>%
  ggplot() +
  geom_map(aes(x = long, y = lat, map_id = region, fill = mortality),map = world) +
  scale_fill_continuous(labels = scales::percent, low   = "green", high  = "red")+
  
  labs(title = "Comfirmed covid deaths in relation to population size")
```

